---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# KingCountyHouses

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/KingCountyHouses)](https://CRAN.R-project.org/package=KingCountyHouses)
<!-- badges: end -->

This package contains housing data in Washington State from 2014-05-02 to 2015-05-27. There are 21,613 data points with 19 columns. 

```{r}
library(KingCountyHouses)
str(home_prices)
```

## Installation

You can install the released version of KingCountyHouses from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("KingCountyHouses")
```

## Code of Conduct
  
Please note that the KingCountyHouses project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
